%--------------------------------------------------
% Resume - Suraj Kumar (v1.2)
%
% Author: Suraj Kumar
% GitHub: https://github.com/ImSurajx
% LinkedIn: https://linkedin.com/in/itsurajx
%
% Description:
% This is a professional resume written in LaTeX.
% The file is version-controlled and will be updated
% as skills, projects, and experience grow over time.
%
% License: MIT
%
% ---------------- HOW TO USE THIS FILE ----------------
%
% 1. If you are new to LaTeX:
%    - Upload this file to Overleaf (www.overleaf.com)
%    - Click "Recompile"
%    - Edit text inside sections (Profile, Skills, Projects, etc.)
%
% 2. How LaTeX Works (Very Basic):
%    - Everything between \begin{document} and \end{document}
%      is the actual resume content.
%    - \section*{Section Name} creates a new section.
%    - \begin{itemize} ... \end{itemize} creates bullet points.
%    - Text inside {} is formatted text.
%
% 3. To Modify:
%    - Replace my name with yours.
%    - Update links in the header.
%    - Edit bullet points carefully.
%    - Do NOT remove formatting commands unless you understand them.
%
% 4. Compile:
%    - Use PDFLaTeX (default in Overleaf).
%
%--------------------------------------------------

\documentclass[a4paper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{color}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%----------MARGINS----------
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.2in}

\setlist[itemize]{noitemsep, topsep=3pt}

\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\begin{document}

%----------HEADING-----------------
% This section contains your name and contact information.
\begin{center}
	{\fontsize{24}{26}\selectfont \textbf{Suraj Kumar}}\\
	\vspace{4pt}
	{\small BCA Student (2023--2026) | Frontend Developer | DSA (C++)}\\
	\vspace{6pt}
	\href{https://github.com/ImSurajx}{github.com/ImSurajx}
	\quad • \quad
	\href{https://www.linkedin.com/in/itsurajx}{linkedin.com/in/itsurajx}
	\quad • \quad
	\href{mailto:surajxcode@gmail.com}{surajxcode@gmail.com}
	\quad • \quad
	\href{tel:+910000099999}{+91 0000000000}
\end{center}

%----------PROFILE-----------------
% Short professional summary (2–4 lines max).
\section*{Profile}

BCA student focused on building logic-driven applications using JavaScript and C++. Strong interest in problem-solving, data structures, and system design. Experienced in debugging complex issues within large Android codebases. Currently developing real-world projects to strengthen core engineering fundamentals and application-level thinking.

%----------PROJECTS-----------------
% Add real projects only with technical clarity.
\section*{Projects}

\begin{itemize}
	
	\item \textbf{PixelForge (Browser-Based Image Editor)} \\
	      Repo: \href{https://github.com/ImSurajx/pixel-forge}{https://github.com/ImSurajx/pixel-forge} \\
	      Live: \href{https://imsurajx.github.io/pixel-forge/}{https://imsurajx.github.io/pixel-forge/} \\
	      \textit{Technologies: JavaScript, HTML5 Canvas, HTML, CSS}
	      
	      \begin{itemize}
	      	\item Built a real-time image editor using HTML Canvas with direct pixel manipulation and live preview rendering.
	      	\item Implemented brightness, contrast, saturation, hue, and exposure adjustment pipelines using JavaScript image data processing.
	      	\item Added rotate, flip, zoom, preset filters, reset/revert controls, and downloadable edited image export functionality.
	      \end{itemize}

    \item \textbf{Kanban Task Management Dashboard (Ongoing Development)} \\
	      Repo: \href{https://github.com/ImSurajx/kanban-dashboard}{https://github.com/ImSurajx/kanban-dashboard} \\
	      \textit{Technologies: JavaScript, HTML, SCSS}
	      
	      \begin{itemize}
	      	\item Built a task management system with multiple state columns (Todo, In Progress, Completed).
	      	\item Managed dynamic task state transitions and DOM updates using JavaScript.
	      	\item Structured task data and state handling to enable scalable updates and future drag-and-drop functionality.
	      \end{itemize}

	\item \textbf{Snake Game (Real-Time Game Logic Implementation)} \\
	      Repo: \href{https://github.com/ImSurajx/snake-game-vanilla-js}{https://github.com/ImSurajx/snake-game-vanilla-js} \\
	      \textit{Technologies: JavaScript, HTML, CSS}
	      
	      \begin{itemize}
	      	\item Built a grid-based game engine with real-time movement and collision detection.
	      	\item Implemented game loop and real-time state updates using setInterval for smooth gameplay.
	      	\item Designed scoring system with food generation and persistent high score tracking.
	      \end{itemize}

\end{itemize}
%----------OPEN SOURCE EXPERIENCE-----------------
% Mention technical impact, not emotional storytelling.
\section*{Open-Source Experience}

\textbf{Android Custom ROM Contributor (Redmi Note 7 - Lavender)} \hfill 6--8 Months

\begin{itemize}
	\item Contributed to Android-based custom ROM development, managing device configurations, kernel integration, and system-level debugging.
	\item Worked with large Android codebases including device trees, vendor configurations, kernel integration, and Linux-based build systems.
	\item Practiced advanced Git workflows such as rebasing, cherry-picking, and resolving complex merge conflicts.
	\item Debugged build failures and optimized configuration issues within CI/CD environments.
	\item Successfully raised highest community crowdfunding contribution to restore development hardware.
	\item Selected as a member of the ROM Builder organization (150+ contributors) after multiple evaluation attempts.
\end{itemize}

%----------TECHNICAL SKILLS-----------------
% List only skills you can confidently explain in interview.
\section*{Technical Skills}

\begin{itemize}
	\item \textbf{Languages:} C++, JavaScript
	\item \textbf{Frontend:} HTML5, CSS3, SCSS
    \item \textbf{Core Concepts:} Data Structures (Arrays, 2D Arrays), Problem Solving, Debugging, DOM Manipulation, Event Handling, Game Logic Design, State Management (UI State Handling)
	\item \textbf{Version Control:} Git, GitHub (Rebasing, Cherry-picking, Conflict Resolution)
	\item \textbf{Tools:} VS Code, Linux Environment
\end{itemize}

%----------EDUCATION-----------------
% Mention degree and university clearly.
\section*{Education}

\textbf{Indira Gandhi National Open University (IGNOU)} \hfill 2023 -- 2026 \\
Bachelor of Computer Applications (BCA)

\end{document}